ms2

### 2017-05-02 ms2/ms2.Rmd
moving to hrr

hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr)

@@

abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by='zipcode') %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

# Keep only those bug/drug combinations that are in at least 20 states
abg %<>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_states=n) %>%
  filter(n_states >= 20) %>%
  left_join(abg, by=c('bug', 'drug_group'))

summarize_abg = function(df, place_name, min_places=20) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}

@@

I consider resistance among these organisms:

`r organisms %>% as.list %>% pander`

@@

I similarly joined the consumption drugs into similar classes.

```{r do_models}
pvalue_stars = function(x) {
  case_when(x < 0.001 ~ '***',
            x < 0.01 ~ '**',
            x < 0.05 ~ '*',
            x < 0.1 ~ 'o',
            TRUE ~ '')
}

linear_model = function(df, dependent_var, explanatory_vars) {
  f = paste0(dependent_var, ' ~ ', paste0(explanatory_vars, collapse = ' + ')) %>% formula
  lm(formula=f, weights=place_weight, data=df) %>%
    tidy %>%
    select(term, estimate, p.value)
}

@@

multivariate_term = 'nzgini'
#multivariate_term = 'mean_fnz_residual'
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  # swo> "mean" is a confusing name
  bind_rows(
    linear_model(x, dep, 'mean') %>% mutate(model='univariate'),
    linear_model(x, dep, c('fnz', multivariate_term)) %>% mutate(model='multivariate'),
    spearman_model(x, dep, 'mean') %>% mutate(model='spearman')
  )
}

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r hrr_univariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r}
sig_bug_drug = results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

@@

```{r hrr_multivariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

>>>>

zipcodes = read_tsv('../../db/zipcode/zipcode.tsv') %>%
  select(zipcode=zip, state)

hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

@@

abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

possible_bug_drug = read_tsv('bug_drug.tsv')

# Keep only bug/drug combinations that are in at least 75 HRRs
good_combos = possible_bug_drug %>%
  left_join(abg, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, hrr) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= 75)

abg %<>% right_join(good_combos, by=c('bug', 'drug_group'))

summarize_abg = function(df, place_name) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}

@@

@@

I similarly joined the consumption drugs into similar classes. I'm looking at these `r nrow(good_combos)` bug/drug combinations:

`r good_combos %>% arrange(desc(n_places)) %>% kable`

```{r do_models}
linear_model = function(df, dependent_var, explanatory_vars) {
  f = paste0(dependent_var, ' ~ ', paste0(explanatory_vars, collapse = ' + ')) %>% formula
  lm(formula=f, weights=place_weight, data=df) %>%
    tidy %>%
    select(term, estimate, p.value)
}

@@

multivariate_term = 'nzgini'
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  # swo> "mean" is a confusing name
  bind_rows(
    linear_model(x, dep, 'mean') %>% mutate(model='univariate'),
    linear_model(x, dep, c('fnz', multivariate_term)) %>% mutate(model='multivariate'),
    spearman_model(x, dep, 'mean') %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

@@

```{r spearman_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj, n_data) %>%
  kable
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj, n_data) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r hrr_univariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r eval=FALSE}
sig_bug_drug = results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

@@

```{r hrr_multivariate_models, cache=FALSE}
sig_bug_drug = hrr_results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  #right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

And for HRRs:

```{r}
left_join(hrr_abg, hrr_ineq, by=c('hrr', 'drug_group')) %>%
  left_join(hrr, by='hrr') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region, size=sqrt(total))) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```
